EasyMerge - Clone Code Refactor

### 2014-03-06 paper/paper.tex
made some changes

\terms{Theory}

\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings

@@

Previous research shows that a significant fraction (between 7\% and 23\%) of the code in a typical software system has been cloned \cite{baker} \cite{roy}. Many code clones
in code bases are unnecessary duplications. By detecting, categorizing,
and removing code clones, we can produce easier to understand, cleaner, and more reusable code.

@@

>>>>

\terms{Software Engineering, Recommendation System}

\keywords{Software Engineering, Clone Detection, Code Refactoring, Recommendation System} % NOT required for Proceedings

@@

Previous research shows that a significant fraction (between 7\% and 23\%) of the code in a typical software system has been cloned \cite{baker} \cite{roy}. Many code clones
in code bases are unnecessary duplications. 
Code duplication can be a significant drawback, leading to bad design, and increased probability of bug occurrence and propagation. As a result, it can significantly
increase maintenance cost, and form a barrier for software evolution. By detecting, categorizing,
and removing code clones, we can produce easier to understand, cleaner, and more reusable code.

@@

More specifically, we pick CloneDigger \cite{bulychev}, an anti-unification duplicate code detection tool as our underlying clone detection approach, for its overall performance, coverage of multiple clone types, and availability. EasyMerge integrates CloneDigger as the pre-processing tool, analyze its output clone pairs, and recommend possible merges which can remove unnecessary clones without changing functionality of code base, creating reference conflicts, nor causing troubles to future code understanding or development.
